---
title: "Smart Grid Fund Survey 2 Findings 15may17"
author: "Ken Deal & Dean Mountain"
date: "15may17"
output:
  html_document: default
  html_notebook: default
---

#Smart Grid Fund Electricity Pilot
##Findings from Survey 2
##Preliminary findings, 8:30am 15may17


```{r "setup", include=FALSE, echo=FALSE, message=FALSE}
require(sjPlot)
require(sjmisc)
require(dplyr)
require(ggplot2)
require(knitr)
opts_knit$set(root.dir ="E:/Sawtooth/SSI Web/FlexPlan_26apr17/Export_15may17/RawExport_15may17")

```

```{r  include=FALSE, echo=FALSE, message=FALSE}
sgf <- read.csv("RawExport_15may17.csv",  sep=",", header=TRUE) # read the data file
dim(sgf)
#head(sgf,3) # view 1st 3 rows of data
sgf[1:3,1:10]
names(sgf)[1] <- "sys_RespNum"
sgf_cov<- sgf[, c(1,4,9, 19:25, 71:82, 311:428, 453:598 )]
dim(sgf_cov)
#describe(sgf_cov)
write.csv(sgf_cov,"sgf_cov.csv",row.names=FALSE)
sgf_elec_opinions<- sgf[,c(1,4,599)]
write.csv(sgf_elec_opinions,"sgf_elec_opinions.csv",row.names=FALSE)
sgf_survey_opinions<- sgf[,c(1,4,600)]
write.csv(sgf_survey_opinions,"sgf_survey_opinions.csv",row.names=FALSE)
str(sgf_cov)

```

```{r include=FALSE, echo=FALSE, message=FALSE}
sgf_cov$egroup  <- recode_factor( sgf_cov$egroup , 
                  `1`='Experiment: No feedback', 
                  `2`='Experiment: IHD, No Energate', 
                  `3`='Experiment: IHD + PlotWatt + No Energate',
                  `4`='Control: No feedback',
                  `5`='Control: IHD + No Energate',
                  `6`='Control: IHD + PlotWatt + No Energate')
sgf_cov$group  <- recode_factor( sgf_cov$group , 
                  `1`='Experiment: No feedback', 
                  `2`='Experiment: IHD, No Energate', 
                  `3`='Experiment: IHD + PlotWatt + No Energate',
                  `4`='Control: No feedback',
                  `5`='Control: IHD + No Energate',
                  `6`='Control: IHD + PlotWatt + No Energate',
                  `9`='Dropped out of pilot')
sgf_cov[,7]  <- recode_factor( sgf_cov[,7] , 
                  `1`='R1', 
                  `2`='R2', 
                  `3`='R3', 
                  .default = NULL, .missing = NULL)
sgf_cov[,10]  <- recode_factor( sgf_cov[,10] , 
                 `1`='H1 TOU', 
                 `2`='TOU1', 
                 `3`='TOU2',
                 `4`='TOU3',
                 `5`='TOU4',
                 `6`='TOU5',
                 `7`='TOU6',
                 `8`='VPP/CPP7',
                 `9`='VPP/CPP8',
                 `10`='VPP/CPP9',
                 `11`='VPP/CPP10',
                 `12`='RTP11',
                 `13`='RTP12', 
                 .default = NULL, .missing = NULL)

```
###Tables of electricity and sample design categories
```{r eval=FALSE, echo=FALSE, message=FALSE}
sjt.frq(sgf_cov$egroup, var.labels=c("egroup"))
```
`r sjt.frq(sgf_cov$egroup, var.labels=c("egroup"), no.output=TRUE)$knitr`


```{r eval=FALSE, echo=FALSE, message=FALSE}
sjt.frq(sgf_cov$group, var.labels=c("group"))
```
`r sjt.frq(sgf_cov$group, var.labels=c("group"), no.output=TRUE)$knitr`  

Group by e-group    

```{r eval=FALSE, echo=FALSE, message=FALSE}
sjt.xtab(sgf_cov[,6], sgf_cov[,8], var.labels=c("group", "egroup"))
```
`r sjt.xtab(sgf_cov[,6], sgf_cov[,8], var.labels=c("group", "egroup"), no.output=TRUE)$knitr`



Rate Groups  
***
```{r eval=FALSE, echo=FALSE, message=FALSE}
sjt.frq(sgf_cov[,7], var.labels=c("rategroup"))
```
`r sjt.frq(sgf_cov[,7], var.labels=c("rategroup"), no.output=TRUE)$knitr`  
  
Treatment Groups
***
```{r eval=FALSE, echo=FALSE, message=FALSE}
sjt.frq(sgf_cov[,10], var.labels=c("treatment"), show.summary=TRUE)
```
`r sjt.frq(sgf_cov[,10], var.labels=c("treatment"), show.summary=TRUE, no.output=TRUE)$knitr`

#### Customer responses to survey questions

```{r  echo=FALSE, message=FALSE}
sgf_cov[,11]  <- recode_factor( sgf_cov[,11] , 
                               `1`='Less electricity used', 
                               `2`='About the same electricity', 
                               `3`='More electricity used', 
                               .default = NULL, .missing = NULL)
```
```{r eval=FALSE, echo=FALSE, message=FALSE}
sjt.frq(sgf_cov[,11], var.labels=c("Conservation Efforts"))
```
`r sjt.frq(sgf_cov[,11], var.labels=c("Conservation Efforts"), no.output=TRUE)$knitr`  

Conservation efforts by group    

```{r eval=FALSE, echo=FALSE, message=FALSE}
sjt.xtab(sgf_cov[,11], sgf_cov[,6], 
         var.labels=c("Conservation Efforts", "group"),
         show.col.prc=TRUE, tdcol.col="black",
         show.obs=TRUE, show.summary = TRUE,
         emph.total=TRUE, emph.color = "lightblue")
```
`r sjt.xtab(sgf_cov[,11], sgf_cov[,6], 
         var.labels=c("Conservation Efforts", "group"),
         show.col.prc=TRUE, tdcol.col="black",
         show.obs=TRUE, show.summary = TRUE,
         emph.total=TRUE, emph.color = "lightblue", no.output=TRUE)$knitr`  

Shifting electricity  
```{r  echo=FALSE, message=FALSE}
sgf_cov[,12]  <- recode_factor( sgf_cov[,12] , 
              `1`='Yes I have shifted electricity usage', 
              `2`='No I have not shifted electricity usage', 
                                .default = NULL, .missing = NULL)
```
```{r eval=FALSE, echo=FALSE, message=FALSE}
sjt.frq(sgf_cov[,12], var.labels=c("Shifting Efforts"))
```
`r sjt.frq(sgf_cov[,12], var.labels=c("Shifting Efforts"), no.output=TRUE)$knitr`  

Shifting efforts by group  

```{r eval=FALSE, echo=FALSE, message=FALSE}
sjt.xtab(sgf_cov[,12], sgf_cov[,6], 
         var.labels=c("Shifting Efforts", "group"),
         show.col.prc=TRUE, tdcol.col="black",
         show.obs=TRUE, show.summary = TRUE,
         emph.total=TRUE, emph.color = "lightblue")
```
`r sjt.xtab(sgf_cov[,12], sgf_cov[,6], 
         var.labels=c("Shifting Efforts", "group"),
         show.col.prc=TRUE, tdcol.col="black",
         show.obs=TRUE, show.summary = TRUE,
         emph.total=TRUE, emph.color = "lightblue", no.output=TRUE)$knitr`

